### 2014-09-11 paper/paper.Rmd
occupation

### b. Parent's Occupation Status
One of the variables the survey addressed was the occupation status of each of the parents. There were five possible categories: “Full-Time”, “Part-Time”, “Not working, but looking for a job”, “Other (e.g. home duties, retired)”, and no response. The frequencies for these categories can be seen in the bar chart. The chart shows that fathers primarily have full-time jobs. However, there are large numbers of mothers who work full-time, part-time, or are stay-at-home moms. With women making up a larger portion of the work-force, it is interesting to look at how the parents' occupations relate to students' performance in math.

The plot below shows the average student math score by the parents' occupational status. The countries are sorted according to the average score for students with a "full-time" mother. Occupational status are distinguished by color.  In each of the plots below, students with mothers who work part-time or full-time tend outperform those students with stay-at-home mothers. This pattern holds with only a few exceptions. Meanwhile, when the father is employed part-time, students tend to have much lower achievement that if the father stayed at home. Those students whose fathers have full-time jobs have the highest average achievement among the possible work statuses for the father. The patterns described hold across mathematics, reading, and science.

>>>>

### b. Parent's Occupation Status
One of the variables the survey addressed was the occupation status of each of the parents. There were five possible categories: “Full-Time”, “Part-Time”, “Not working, but looking for a job”, “Other (e.g. stay-at-home, retired)”, and no response. The frequencies for these categories can be seen in the bar chart. The chart shows that fathers primarily have full-time jobs. However, there are large numbers of mothers who work full-time, part-time, or are categorized as "Other". With women making up a larger portion of the work-force, it is interesting to look at how the parents' occupations relate to students' performance in math.

The plot below shows the average student math score by the parents' occupational status. The countries are sorted according to the average score for students with a mother who is "full-time" in the work force. Occupational status is distinguished by color.  Students with mothers who work part-time or full-time tend outperform those students with mothers labelled as "Other". This pattern holds with only a few exceptions, Switzerland, Netherlands, USA, Japan. Meanwhile, when the father is employed part-time, students tend to have much lower scores that if the father labelled as "Other". Those students whose fathers have full-time jobs have the highest average scores among the possible work statuses for the father. The patterns described also hold across reading and science.
